A Pedestrian Simulation

### 2014-11-23 doc/informe/paper.tex
estandarizo todas las imagenes del papaer (re hice todas con ppt). cambio detalles varios en el paper.

\title{A Pedestrian Simulationnnnnn}

@@

\subsection{Motivacion y antecedentes}

@@

En el Social Force Model cada peatón se rige por una serie de reglas
presentads por Helbing en sus paper {[}Helbing 1995, 2000{]}. A partir
de estas reglas, proupso un modelo en donde cada peatón sufre una
fuerza de deseo que lo provoca a acercarse hacia su objetivo y una
fuerza de repulsión contra cada uno de los demas peatones. Junto a
estas dos, existe la fuerza de contacto producto del conectacto físico.
\\

Cada una de las fuerzas en el modelo se define usando las siguientes
fórmulas:\\

Fuerza de contacto (Granular):

@@

En donde: $\epsilon_{ij}=r_{ij}-(R_{i}+R_{j})$

@@

Fuerza social:
\[
F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
\]

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.6]{sfm/sf}
\par\end{centering}

\protect\caption{Fuerza social}
\end{figure}

Fuerza de deseo:

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.7]{sfm/drivingforce}
\par\end{centering}

@@

Luego, se calcula $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$

En donde los parametros se encuentran definidos con lo siguientes
valores: $A=2000\,[N]$, $B=0.08\,[m]$, $k_{n}=1.2\,10^{5}\,[\frac{N}{m}]$,
$k_{t}=2.4\,10^{5}\,[\frac{kg}{m/s}]$ y $\tau=0.5\,[s]$.

\subsection{Future Vector Particle Model}

Debido a que el SFM presenta una fuerza ficticia sobre el peatón,
se generan artificios en la navegación ante la presencia de grandes
cantidades de peatones. \{...\}

Frente a esto se presenta un nuevo modelo

// no reproduce valores de Caudal Específico ni Diagrama Fundamental

// To do: explicar nuestros aportes al modelo, observaciones sobre
el SFM\\

@@

In the following the main effects that determine the motion of a pedestrian
will be introduced: (agregar que son las mismas hipotesis que presenta
Helbin en su paper)
\begin{enumerate}
\item The pedestrian wants to reach to his goal in the shortest possible
path.
\item The pedestrian's movement is influenced by other pedestrians. Depending
on the distance between the two of them and the predicted trayectory,
the pedestrian will feel the need to change his route to be able to
avoid the other pedestrian. It is because of this effect that pedestrians
will need to recalculate their route as new pedestrians get closer
to them.
\item Movement speed will be influenced by needs.
\end{enumerate}

\subsection{??}

@@

\item Short term objective
\item Objetivo a corto plazo

@@

\subsection{Implementation}

@@

\[
F_{deseo}=\frac{dist(i',i)}{dist_{react}}\frac{v_{desire}-v_{curr}}{\tau}\frac{i'-i}{|i'-i|}
\]

Where $\tau=0.5$

\item Pedestrian position update.

@@

\end{enumerate}
\end{enumerate}
TODO: Los valores que se usaron son $\alpha=800$ y $\beta=[0.65,\,085]$
con distribución uniforme.

\section{Calibracion}

\subsection{Metricas a usar}

Los resultados obtenidos fueron comparados utilizando el modelo ``Social
Force Model'' utilizando los valores propuestos por Dirk Helbing
{[}2{]}. Los escenarios de prueba fueron cruce y hallway.

Los resultados fueron cuantificados utilizando las siguientes métricas:
\begin{enumerate}
\item Cantidad total de colisiones

TODO: (como se calcula)

\item Duración promedio de las coliciones

TODO: (como se calcula)

\item Velocidad promedio de viaje

TODO: (como se calcula)

\item Tiempo promedio de viaje

TODO: (como se calcula)

\item Promedio de la distancia recorrida

TODO: (como se calcula)

\item Ángulo giro promedio

TODO: (como se calcula)

@@

@@

\vspace{1cm}
En la tabla a continuación se presentan las mediciones de las métricas
utilizando un total de $10$ corridas:

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Valores & 1 & 2 & 3 & 4 & 5 & 6\tabularnewline
\hline 
\hline 
$\alpha=800,\,\beta=[0.65,\,0.85]$ & (1.800, 0.748)  & (34.600, 8.333)  & (1.024, 0.016)  & (1.910, 0.022)  & (2.392, 0.005)  & (111.062, 19.122)\tabularnewline
\hline 
$\alpha=2000,\,\beta=0.08$ & (5.333, 2.625) & (12.333, 8.340)  & (1.052, 0.003)  & (1.876, 0.003)  & (2.391, 0.002)  & (106.185, 13.778)\tabularnewline
\hline 
\end{tabular}

@@

\section{Conclusiones}

@@

\section{Referencias}
\begin{itemize}
\item {[}1{]} ... Karamouzas ...
\item {[}2{]} ...Helbing ...\end{itemize}

>>>>

\title{A Pedestrian Simulation}

@@

\subsection{Motivation and previous work}

@@

{[}Helbing 1995, 2000{]} presents a Model in which each pedestrian
feels a ``desire force'' towards his objective and a ``repulsion
force'' towards other pedestrians. On a lower level, a collission
force is present.

Collision force (Granular):

@@

Where: $\epsilon_{ij}=r_{ij}-(R_{i}+R_{j})$

@@

Social Force:
\[
F_{S_{i}}=\sum_{j=1,j\ne i}^{N_{P}}Aexp(-\frac{\epsilon_{ij}}{B})\, e_{ij}^{n}
\]

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.4]{sfm/sf}
\par\end{centering}

\protect\caption{Social Force}
\end{figure}

Desire Force:

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.4]{sfm/drivingforce}
\par\end{centering}

@@

Afterwards $F_{i}=F_{G_{i}}+F_{S_{i}}+F_{D_{i}}$is calculated

Fixed parameter values: $A=2000\,[N]$, $B=0.08\,[m]$, $k_{n}=1.2\,10^{5}\,[\frac{N}{m}]$,
$k_{t}=2.4\,10^{5}\,[\frac{kg}{m/s}]$ y $\tau=0.5\,[s]$.

While this model doesn't present a very real behaviour for pedestrians,
it worked as a starting point for numerous projects.

\subsection{Future Virtual Particle Model}

Given that the SFM adds a fictional force on pedestrians, navigation
stops imitating reality when there's a big quantity of pedestrians.
Pedestrians also show a collision avoidance method that resembles
magnetism, with movements that are clearly governed by the squared
distance to the other pedestrian. Also, SFM didn't have the same values
as well known metrics for real-case scenarios such as the flow of
pedestrians going out a door and the fundamental diagram.

Because of this, we present a new model.

@@

The main effects that govern the motion of a pedestrian are the same
as Helbin's:
\begin{enumerate}
\item The pedestrian wants to reach his goal in the shortest possible path.
\item The pedestrian's movement is influenced by other pedestrians. Depending
on the distance between the two of them and the predicted trayectory,
the pedestrian will feel the need to change his route to be able to
avoid the other pedestrians. It is because of this effect that pedestrians
will need to recalculate their route as new pedestrians get closer
to them.
\item Movement speed will be influenced by needs.
\end{enumerate}

\subsection{Definition}

@@

\item Short term objective

@@

\subsection{Algorithm}

@@

\[
F_{desire_{i}}=m_{i}\frac{\frac{dist(i',i)}{dist_{react}}e_{i}-v_{i}}{\tau}
\]

Where $\tau=0.5$
\begin{enumerate}
\item Pedestrian position update.

@@

\end{enumerate}
\end{enumerate}

\section{Calibration}

\subsection{Metrics}

The results where compared to the SFM using the values propposed by
Dirk Helbing {[}2{]}. The test scenarios where crossing and hallway
for they present the main two types of simmetry (90 degrees and 180
degrees).

The metrics used where:
\begin{enumerate}
\item Number of collisions

When a pedestrian's body is touching another one, a counter is incremented,
it won't be incremented again unless it separates and touch again.
This counter represents the amount of collisions.

\item Total duration of collisions:

When a pedestrian's body is touching another one, a counter is incremented
by the time step of the simulation. This counter will represent the
total time pedestrians were colliding.

\item Average walking speed:

//TODO

\item Average travel time:

When a pedestrian appears in the map, this time is recorded, once
he reaches his goal, the travel time is calculated with this value.
The average of all this times represents the average travel time.

\item Average travel distance:

Each step, the distance a pedestrian has traveled from the source
is saved. When this pedestrian reaches his goal, that distance is
considered as finished and it is saved elsewhere. Afterwards, an average
of all finished distances is calculated.

\item Average turn angle:

Each step, the angle of the previous velocity of a pedestrian and
the current one is saved and added to a total. When this pedestrians
reaches his goal, this total is considered as finished and it is saved
elsewhere. Afterwards, an average of all finished turn angles is calculated.

@@

\subsection{Values}

To calibrate the model, runs varying parameters were made. A wide
spectrum of values was covered, testing every combination of every
possible one. After seeing clear preferences towards certain values,
the values were refined within that scope. After numerous iterations
of this process, the values that best suit these metrics are$\alpha=800$
y $\beta=[0.65,\,085]$ uniformly distributed.

//TODO todos los demás parámetros

@@

\begin{table}[H]
{\scriptsize{}}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
{\scriptsize{}Values} & {\scriptsize{}1} & {\scriptsize{}2} & {\scriptsize{}3} & {\scriptsize{}4} & {\scriptsize{}5} & {\scriptsize{}6}\tabularnewline
\hline 
\hline 
{\scriptsize{}$\alpha=800,\,\beta=[0.65,\,0.85]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
\hline 
{\scriptsize{}$\alpha=2000,\,\beta=0.08$} & {\scriptsize{}(5.333, 2.625)} & {\scriptsize{}(12.333, 8.340) } & {\scriptsize{}(1.052, 0.003) } & {\scriptsize{}(1.876, 0.003) } & {\scriptsize{}(2.391, 0.002) } & {\scriptsize{}(106.185, 13.778)}\tabularnewline
\hline 
\end{tabular}\protect\caption{Metrics comparing SFM vs FVPM. Average of $10$ runs.}
\end{table}

@@

\section{Conclusions}

@@

\section{References}
\begin{itemize}
\item {[}1{]} ... Karamouzas ...
\item {[}2{]} ...Helbing ...\end{itemize}
